
\documentclass[11pt,a4paper,roman]{moderncv}      
\usepackage[english]{babel}
\usepackage{ragged2e}
\usepackage{float}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}   

\moderncvstyle{classic}                            
\moderncvcolor{green} % Bullet point color                          

% Page margins
\usepackage[scale=0.8]{geometry} % Page margins

% Your Information, please revise
\name{Sweta Parna}{Nayak}
\address{Enschede, Netherlands}
\phone[mobile]{(+31) 6 30671282}                   
\email{s.p.nayak@student.utwente.nl}             
                   
\begin{document}

\begin{minipage}[t]{\textwidth}
\end{minipage}

\recipient{Dear Hiring Manager,}{
Applying for the role of Consumer & Proposition Insights Manager}
\opening{\vspace*{-2em}}
\closing{Sincerely,}{\vspace*{-2em}}
\enclosure[Enclosures]{Resume, Cover Letter}   
\makelettertitle

\justifying

With a Master's in Public Administration and over three years of experience in policy analysis, sustainability reporting, and project management, I am excited about the opportunity to contribute to ClimatePartner's mission of helping businesses integrate sustainability and circularity policy into their strategies. My key competencies include:

- Regulatory Compliance
- Lifecycle Assessment
- Policy Analysis
- Data Analysis
- Sustainable Finance Reporting
- Public Relations
- Project Management
- Stakeholder Management

I have a comprehensive understanding of governance and compliance patterns and have conducted extensive policy analysis, corrections, and maintained strong stakeholder communication. I am skilled in designing and implementing policies combined with risk mitigation techniques. My proactive approach and proven track record in sustainability and policy analysis align well with the responsibilities of the Consultant position at ClimatePartner. I am eager to contribute to the mission of creating impactful communication strategies.

I have utilized analytical tools like Excel and PowerBI to analyze financial fronts of policies, their impact, deficits, and how they could be bridged. I have used management tools like Trello and Asana to collaborate with stakeholders for timely deliverables. My experience in international and multicultural contexts, coupled with my strong interpersonal skills, makes me confident in my ability to engage with EU institutions, businesses, and civil society. 

Thank you for considering my application. I look forward to the opportunity to discuss how my background, skills, and passion for sustainability can benefit ClimatePartner.

\vspace{0.5cm}

\makeletterclosing

\end{document}
