
\documentclass[letterpaper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.4in}
\addtolength{\evensidemargin}{-0.4in}
\addtolength{\textwidth}{0.8in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-1pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
\textbf{\Huge \scshape Sweta Parna Nayak} \\ 
\small (+31) 6 30671282 $|$
\href{mailto:s.p.nayak@student.utwente.nl}{\underline{s.p.nayak@student.utwente.nl}} $|$
\href{https://www.linkedin.com/in/sweta-parna-nayak-783736195}{\underline{LinkedIn}} $|$
Enschede, Netherlands
\end{center}


%-----------Objective-----------
\section{Objective}


A dedicated and experienced professional with a proven track record in data analysis, market research, and consumer behavior analysis. Seeking a Consumer & Proposition Insights Manager role where I can drive consumer centricity, manage end-to-end consumer research, and translate data into actionable insights to enhance product propositions. Committed to continuous learning, innovation, and delivering superior propositions to increase consumer engagement and drive business performance.

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Partner Compliance Screening Intern}{Amsterdam, NL}
{Philips International B.V (philips.nl)}{Oct 2023 to Apr 2024}
\resumeItemListStart
\resumeItem{Directed market investigations in the Indian Subcontinent to bolster brand protection and reduce operational risks}
\resumeItem{Aligned investigations with EU Taxonomy, CSRD, GRI, and OECD standards, ensuring detailed client information is sourced for enhanced ethical compliance.}
\resumeItem{Developed a methodology to integrate these standards into the due diligence process.}
\resumeItemListEnd

\resumeSubheading
{Associate, Political Research and Strategy}{India}
{Showtime Consulting Inc. (showtimeconsulting.in)}{Feb 2022 to Jan 2023}
\resumeItemListStart
\resumeItem{Researched and designed roadmaps for political campaigns (TDP, NPP) leading up to a landslide victory in the Indian General elections 2024.}
\resumeItem{Analyzed welfare policies for the Indian states of Andhra Pradesh \& Meghalaya (57M people) to identify financial gaps and recommend recovery methods, comparing allocated funds to actual benefits received.}
\resumeItem{Prepared and distributed press releases and documented internal communication reports.}
\resumeItem{Maintained constant communication with field project partners and suppliers, ensuring smooth project execution.}
\resumeItemListEnd

\resumeSubheading
{Associate Content Lead}{India}
{NIIT Limited (niit.com)}{Aug 2021 to Jan 2022}
\resumeItemListStart
\resumeItem{Developed web-based and instructor-led training modules for massive online courseware (MOOCs) such as Coursera.}
\resumeItem{Managed the lifecycle of the end-to-end content management process and mentored 6 content analysts.}
\resumeItemListEnd

\resumeSubheading
{Policy and Project Associate}{India}
{Office of the Member of Parliament, Govt. of India (rajyavardhanrathore.in)}{Sep 2020 to Jun 2021}
\resumeItemListStart
\resumeItem{Led sustainable agriculture and community projects in two Rajasthan villages, boosting local livelihoods.}
\resumeItem{Conducted over 60 stakeholder interviews to shape development strategies and crafted a 200+ question database for local governance.}
\resumeItem{Authored a gram panchayat (rural) development plan with 150+ action items, published on the eGram Swaraj portal.}
\resumeItem{Forged key partnerships to enhance project sustainability and job creation.}
\resumeItemListEnd

\resumeSubheading
{Intern, Social Worker}{India}
{Bombay Mothers and Children Welfare Society (thebmcws.com)}{Jan 2019 to Feb 2019}
\resumeItemListStart
\resumeItem{Conducted case studies for 20 children with cancer to analyze and address family needs.}
\resumeItem{Developed an engaging, fun-filled educational model to aid children's recovery.}
\resumeItemListEnd

\resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University of Twente}{Netherlands}
{MSc in Public Administration; CGPA: 7.14/10}{Feb 2023 to Aug 2024}
\resumeSubheading
{Young India Fellowship, Ashoka University}{India}
{Postgraduate Diploma in Strategic Leadership; CGPA: 3.38/4.0}{Sep 2020 to Jul 2021}
\resumeSubheading
{Tata Institute of Social Sciences}{India}
{Bachelor of Arts (Hons.) in Social Work; CGPA: 6.8/10.0}{Jun 2017 to Apr 2020}
\resumeSubHeadingListEnd


%-----------Skills and Interests-----------
\section{Key Competencies \& Interests}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
\vspace{1mm}
\textbf{Analytical Skills}{: Data Analysis, Consumer Behavior Analysis, Market Research, Data Synthesis, Quantitative Research, Insights Generation, Strategic Analysis, Competitive Analysis, Trend Analysis, Consumer Insights} \\ \vspace{1mm} 
\textbf{Technical Skills}{: PowerBI, MS Excel, Questionnaire Development, Fieldwork Management, Data Analysis, Market Research Tools, Insights and Analytics Platforms, Experimentation Tools, Consumer Proposition Development, Fact-Based Decision Making} \\ \vspace{1mm}
}}
\end{itemize}
\begin{center}
\end{center}
\end{document}
    